Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-25 Manuscript/manuscript.tex
moved accuracy edit to end of paragraph

The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak. \textcolor{blue}{(Analysis of accuracy correlations is included in the supplementary materials.)} Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks. Even if we optimistically take all data together as suggesting a robust correlation in reaction times from one task to another, the mean correlation over the three tasks is only $r = 0.2$, implying that this correlation accounts for  $R^2 = 0.04 = 4\%$ an individual's performance.

>>>>

The results show that the correlations between the strategy metrics in the three tasks (Figure \ref{fig:all_the_cor}) are weak. Perhaps even more surprisingly, there is also little evidence for meaningful correlations between reaction times in the different tasks. Even if we optimistically take all data together as suggesting a robust correlation in reaction times from one task to another, the mean correlation over the three tasks is only $r = 0.2$, implying that this correlation accounts for  $R^2 = 0.04 = 4\%$ an individual's performance. \textcolor{blue}{(Analysis of accuracy correlations is also weak, and is included in the supplementary materials.)}
